---
title: "Lab 02 - Plastic waste"
author: "Insert your name here"
date: "Insert date here"
output: github_document
---

## Load packages and data

```{r load-packages, message=FALSE}
library(tidyverse) 
```

```{r load-data, message=FALSE}
plastic_waste <- read.csv("data/plastic-waste.csv")
```

## Exercises

### Exercise 1

Remove this text, and add your answer for Exercise 1 here.

```{r plastic-waste-continent}
ggplot(data = plastic_waste, 
       mapping = aes(x = plastic_waste_per_cap, 
                     color = continent, 
                     fill = continent)) +
  geom_density(alpha = 0.7)

```

### Exercise 2

```{r plastic-waste-density}
ggplot(data = plastic_waste, aes(x = plastic_waste_per_cap)) +
  geom_histogram(binwidth = 0.2)

plastic_waste %>%
  filter(plastic_waste_per_cap > 3.5)

plastic_waste %>%
  filter(plastic_waste_per_cap < 3.5) %>%
ggplot(mapping = aes(x = plastic_waste_per_cap, 
                     color = continent, fill = continent)) +
  geom_density(alpha = 0.3)
```

### Exercise 3

The violin plot makes the one point that is above 3 in North America more noticeable. In the box plot you could easily not see the one point which later could cause problems. With the violin plot it is very clear that the one point stands out from the rest of the data.

### Exercise 4

Remove this text, and add your answer for Exercise 4 here.

```{r plastic-waste-violin}
# insert code here
```

### Exercise 5

Remove this text, and add your answer for Exercise 5 here.

```{r plastic-waste-mismanaged}
ggplot(data = plastic_waste, 
       mapping = aes(x = mismanaged_plastic_waste, 
                     y = plastic_waste_per_cap, 
                     color = continent))+
 geom_point()
```

### Exercise 6

Remove this text, and add your answer for Exercise 6 here.

```{r plastic-waste-mismanaged-continent}
# insert code here
```

### Exercise 7

Remove this text, and add your answer for Exercise 7 here.

```{r plastic-waste-population-total}
# insert code here
```

```{r plastic-waste-population-coastal}
# insert code here
```

### Exercise 8

Remove this text, and add your answer for Exercise 8 here.

```{r recreate-viz}
# insert code here
```


